Filtering figure

### 2020-05-06 main_figures/filtering.Rmd
renamed pca filters

```{r, include=FALSE}
# requires old pipeComp version
devtools::load_all("pipeComp_biorxiv/pipeComp/")
```

```{r figure2, fig.width=8, fig.height=8.5}
res <- readRDS("../data/results_filtering.rds")
m <- scrna_evalPlot_filtering(res, returnTable=TRUE)
m$doubletRemoval <- !grepl("doubletmethod=none;", m$method)
m$filter <- factor(sapply(strsplit(as.character(m$method),"\\.|="), FUN=function(x) rev(x)[1]),
                     c("nofilter","lenient","default","pca","pca2","stringent","veryStringent"))
cols <- c("black", pipeComp::getQualitativePalette(length(levels(m$filter))-1))
names(cols) <- levels(m$filter)

>>>>

```{r, include=FALSE}
# requires old pipeComp version
devtools::load_all("../../pipeComp_biorxiv/pipeComp/")
```

```{r figure2, fig.width=8, fig.height=8.5}
res <- readRDS("../data/results_filtering.rds")
m <- scrna_evalPlot_filtering(res, returnTable=TRUE)
m$doubletRemoval <- !grepl("doubletmethod=none;", m$method)
m$filter <- factor(sapply(strsplit(as.character(m$method),"\\.|="), FUN=function(x) rev(x)[1]),
                     c("nofilter","lenient","default","pca","pca2","stringent","veryStringent"))
levels(m$filter)[4:5] <- c("pca.all","pca.sel")
cols <- c("black", pipeComp::getQualitativePalette(length(levels(m$filter))-1))
names(cols) <- levels(m$filter)
